\chapter{CONCLUSION \& FUTURE WORK}
\label{ch:conclusion}

Cryptographic implementations form the practical boundary between formal security guarantees and deployed systems. A protocol may be mathematically sound, but its real-world security depends on whether the implementation correctly realizes the intended computation, whether security-critical cryptographic code can be identified, and whether testing methods can expose implementation-level errors before deployment. The works presented in this dissertation advance these goals by developing systematic evaluation, automated checking, and binary-level testing techniques for cryptographic software.

The first contribution studies cryptographic function identification in binaries and provides a comprehensive evaluation of existing approaches for detecting cryptographic algorithms in compiled programs. This work conducts reproduction and replication studies, organizes the design space of existing tools, and develops a unified benchmarking framework that supports more consistent comparison across different approaches. The evaluation covers modern cryptographic algorithms, microbenchmarks, libraries, and large applications, while also accounting for practical variations introduced by compilers, optimization levels, obfuscation strategies, operating systems, and algorithm versions. This work clarifies the current state of cryptographic function identification and provides a benchmark foundation for evaluating future detection techniques in a more systematic and reproducible way.

The second contribution introduces \snarkprobe, an automated security analysis framework for zkSNARK implementations. \snarkprobe targets cryptographic logic errors that are difficult to detect through ordinary testing because a program may still generate proofs, verify proofs, or produce plausible outputs while failing to enforce the intended statement. Rather than only checking for crashes or successful proof generation, \snarkprobe checks whether the implementation is consistent with the expected proof statement. It combines constraint checking, fuzzing-based testing, value monitoring, and error localization to inspect both proof programs and zkSNARK libraries. By identifying inconsistencies across the constraint system, witness generation, and verification logic, \snarkprobe reduces the manual effort required to analyze complex zkSNARK implementations and provides a practical framework for improving confidence in zero-knowledge proof software.

The third contribution develops \greyboxfuzz, a black-box and grey-box differential fuzzing framework for zero-knowledge proof binary applications. \greyboxfuzz addresses the deployed setting where source-level assumptions may be insufficient and where the executable itself must be tested. It uses the expected cryptographic statement as the oracle, identifies security-relevant execution behavior, and localizes inconsistencies across the major components of the proof workflow. By combining structured input generation, cryptographic-input-aware coverage analysis, control-dependency-aware taint tracking, and differential checking, \greyboxfuzz moves binary testing beyond general crash detection and toward detecting logic-level errors in zero-knowledge proof applications.

Future work can extend these research directions in two major ways. First, the current analysis frameworks can be expanded to support a broader range of zero-knowledge proof protocols beyond zkSNARKs, such as zkSTARKs, Bulletproofs, and Plonk-based systems. Different proof systems use different arithmetization methods, transcript structures, polynomial commitment schemes, and verification procedures, so extending the analysis to these protocols would help evaluate whether similar implementation-level weaknesses appear across a wider zero-knowledge ecosystem. Second, future work can further incorporate formal verification to provide stronger assurance for critical components of cryptographic implementations. This direction complements fuzzing-based analysis because fuzzing offers broad compatibility with real-world software artifacts and requires less protocol-specific understanding, while formal verification can establish stronger correctness guarantees when precise specifications are available. Combining these approaches can support practical testing across diverse implementations together with rigorous reasoning about selected security-critical components.



Second, future work can further incorporate formal verification to provide stronger assurance for critical components of cryptographic implementations. This direction is complementary to fuzzing-based analysis because the two approaches offer different advantages. Fuzzing provides greater compatibility with real-world software artifacts and requires less protocol-specific understanding, making it practical for testing diverse implementations, deployed binaries, and systems where complete formal specifications are difficult to obtain. Formal verification, in contrast, can provide stronger correctness guarantees for selected algorithms, protocols, or components once precise specifications are available. Integrating these techniques would support a more comprehensive methodology: fuzzing can broadly test heterogeneous cryptographic software with relatively low specification requirements, while formal verification can establish stronger guarantees for security-critical components that are suitable for rigorous specification and proof.


Overall, reliable cryptographic software requires attention to the gap between intended cryptographic behavior and actual implementation behavior. Even when a protocol is well designed, implementation errors can still affect how security-critical logic is executed, how inputs are validated, and how proof-related computations are enforced. Practical analysis techniques therefore play an important role in identifying inconsistencies that ordinary testing may miss. Strengthening these techniques can improve confidence in cryptographic software and support the development of more secure real-world systems.