\ProvidesFile{ap-bugs}[2025-01-28 bugs appendix]

\makeatletter
\newcommand{\bug}[2]
  {%
    \vspace{6pt}
    \noindent
    {%
      \bfseries
      \ifthen{\equal{high}{#2}}{\color{red}}%
      \ifthen{\equal{low}{#2}}{\color{blue}}%
      \ifthen{\equal{answered}{#2}}{\color{black}}%
      \ifthen{\equal{done}{#2}}{\color{black}}%
      \ifthen{\equal{fixed}{#2}}{\color{black}}%
      \ifthen{\equal{wait}{#2}}{\color{black}}%
      \ifthen{\equal{not}{#2}}{\color{gray}}%
      {\fontsize{9}{10}\reset@font\bf BUG}
      #1.
    }%
    \ignorespaces
  }
\makeatother

\chapter{BUGS}
\ix{bugs//Bugs appendix}

This appendix lists all bugs/comments/issues/etc\@.
under the generic name `bug'.
Each bug is assigned a number when I learn of it.
Bug numbers are 1, 2,~\ldots~.
I started keeping track of bugs in this fashion on February 26, 2022,
and some previously known bugs are included in this list.
A color indicates a bug's priority:

\begin{tabular}{@{}ll@{}}
  \toprule
  \bf Description& \bf Color\\
  \midrule
  done or waiting on someone else& \color{black}black\\
  high priority or easy to do& \color{red}red\\
  low priority& \color{blue}blue\\
  not prioritized yet& \color{gray}gray\\
  \bottomrule\\
\end{tabular}

See the
|ap-bugs.tex|
file
for the \LuaLaTeXLogo\ input
for this appendix.


\section{These bugs need to be looked at}

% I need to fix the following things in \PurdueThesis.
% They are listed in bug number order.

\bug{1}{high}
Table of Contents is double-spaced instead of 1\sfrac12 spacing.
{\small
  Tighten up section and less significant headings spacing?
  Reported by Anita Adams Sale on 2021-03-17.%
}

\bug{6}{not}
APA reference style indents references too far on left.
{\small
Reported by Mark Senn on 2021-04-08.%
}

\bug{8}{not}
Use, for example, |Last Accessed: yyyy-mm-dd.| urldate in bibliography.
{\small
  Reported by Mark Senn on 2021-04-19.%
}

\bug{13}{low}
Headings containing a SmallCaps font do not work.
{\small
  Reported by Javad (Nima) Darivandpour on 2021-06-29.
  See \ref{section-headings-with-smallcaps-font}.%
}

\bug{14}{low}
On Overleaf only,
when using
|\def\ZZshowtimestamp{true}|,
the time and sometimes the date
are wrong at the top of the page.
{\small
  Reported by Mark Senn on 2022-02-25.%
}

\bug{15}{not}
Left reference section margin is ok if a person has 10--99 references.
{\small
  Figure out how to adjusting margin for 1--9 or over 99 references.
  Reported by Mark Senn on unknown date.
}

\bug{19}{high}
|Bibliography| and |References| missing from navigation panel.
{\small
  Reported by Mark Senn on 2022-02-28.
  REFERENCES was in navigation panel on 2022-08-26.
}

\bug{20}{high}
|Bibliography| and |References| should be in all caps.
{\small
  Reported by Mark Senn on 2022-02-28.
  REFERENCES was in all caps on 2022-08-26.%
}

\bug{21}{low}
IE students should be able
to specify IEEE
or APA bibliography format.
{\small
  Reported by Patrick Brunese on 2022-03-04.%
}

\bug{24}{high}
Add |A Dissertation Proposal| document type.
Add |A Thesis Proposal| document type.
{\small
  Reported by Mark Senn on 2022-12-20.%
}

\bug{25}{high}
Dissertations and theses should continue to have
\Place{Month} \Place{year} where \Place{Month} is
|August|, |December|, or |May|.
For everything except dissertations and theses allow
\Place{Month} \Place{year}
or
\Place{Month} \Place{day}|, |\Place{year}
dates where \Place{Month} is any month.
{\small
  Reported by Mark Senn on 2022-12-20.%
}

\bug{26}{high}
Complete |HOW TO DEBUG| \LaTeX\ |PROBLEMS| chapter.
{\small
  Reported by Mark Senn on 2023-01-11.%
}

\bug{28}{high}
Move |\addbibresource|
from |PurdueThesis.cls|
to |thesis.tex|
to be more user friendly.
{\small
  Reported by Panos Manganaris on 2023-06-15.%  Panayotis Thalis Manganaris <pmangana@purdue.edu>
}

\bug{29}{high}
Main biblioography and chapter bibliography should be indented the same amount.
{\small
  Reported by Panos Manganaris on 2023-06-15.%  Panayotis Thalis Manganaris <pmangana@purdue.edu>
}

\bug{30}{low}
Main bibliography and chapter bibliography should both be flush with the left margin.
{\small
  Reported by Mark Senn on 2023-06-19.%
}

\bug{31}{high}
There needs to be way to put a list of publications in a publications section.
{\small
  Reported by Panos Manganaris on 2023-06-14.  %  Panayotis Thalis Manganaris <pmangana@purdue.edu>
  Mark Senn is working on a way to do that
  using
  |keywords = {publication}|
  in a \BibLaTeXLogo\ |.bib| file entry.
}

\bug{33}{low}
Create Color Vision Deficiency (CVD) Accessible Line Graphs.\\
{\small
  IEEE Author Center <ieee-author-center@deliver.ieee.org> wrote on 2024-03-20:
  \begin{quote}
    Approximately 1 in 12 men
    and 1 in 200 women
    have color vision deficiency.
    It is highly likely
    that someone reading your article
    may have difficulty distinguishing between red and green,
    blue and green,
    or yellow and red.
    The following tips will help you communicate better with those readers.
    \begin{itemize}
      \item
        Use both color and shape to convey the same meaning;
        for example,
        solid and dashed lines
        or different fill patterns can help readers understand the figure
        without relying solely on color
      \item
        Each line of your line graph
        should be a thick line with a unique data point symbol.
        Contrast different elements of the figure with both color and brightness
      \item
        Connect the data label
        to the data line
        rather than relying on a color key
    \end{itemize}
    A quick way to evaluate your figure is to print it out in greyscale
    and see if it can still be interpreted correctly;
    if not,
    use some of these tips to more effectively communicate with all readers.
  \end{quote}
  Lisa Renee Williams <will2922@purdue.edu> of the Graduate School wrote on 2024-03-21:
  \begin{quote}
    I think this is a wonderful idea and am in support of including information
    within the template to provide students the opportunity to use CVD.
  \end{quote}
}

\bug{34}{low}
Implement |\begin{chapterabstract}|
and |\end{chapterabstract}|
for abstracts within chapters.
Maybe rename this |paperabstract|?\\
{\small
  Reported by Mark Senn on 2024-04-09.
}

\bug{36}{low}
Improve the order of thesis parts error message
to indicate that not all parts listed are required.
{\small
  Reported by Mark Senn on 2022-09-21.%
}

\bug{37}{low}
Check the spacing after all chapter and non-chapter headings
for consistency.
{\small
  Reported by Mark Senn on 2020-02-28.%
}

\bug{38}{low}
Add short caption info to documentation.
{\small
  See
  \href{https://www-chicagomanualofstyle-org.ezproxy.lib.purdue.edu/book/ed17/part1/ch03/psec040.html}{Shortening captions for a list of illustrations}
  for a suggestion regarding this.
  To do this in \LaTeXLogo\ do\hfil\break
  \begin{quote}
    |\caption[short caption]{long caption}|
  \end{quote}
  Reported by Mark Senn on 2023-12-08.%
}

\bug{39}{low}
Page links for longtables don't link to right place
from List of Tables.
{\small
  Example: Table R.6.
  Reported by Tunazzina Islam on 2025-01-27.%
  {\it This may work with \(\text{hyperref.sty} > 7.01\text h\) in \TeXLiveLogo\ 2025.}
}


\section{These bugs are waiting on a reply from someone other than Mark Senn}

\bug{10}{wait}
Using
|linktoc = section|
does not work with captions with
|\frac|.
{\small
  Reported by Mark Senn on 2021-05-27.
  In the short-term,
  check with Ashlee Messersmith
  if {\tt linktoc = page} can be used.
  If that's ok make the change
  and look into changing captions from my code
  to \LaTeXLogo's code.
  Waiting on Ashlee Messersmith.
}


\section{These bugs have been answered, fixed, or rejected}

\bug{2}{done}
List of Figures indented $\approx$\sfrac14 inch
more than List of Tables.
{\small
  Reported by Anita Adams Sale on 2021-03-17.
  Still happening on 2021-11-30.
  Looked ok on 2022-08-26
  but I think this problem is probably intermittent.
  Keep Ashlee Messersmith,
  Anita Adams Sale,
  and Sherrie Tucker informed.
  Adam Behnke sent me the solution to this problem on 2023-03-27.
}

\bug{3}{done}
Use ``Last Accessed: dd/mm/yy.'' urldate in bibliography.
{\small
  Reported by Priyank Kalgaonkar on 2021-04-06.
  Answered by Mark Senn on 2022-02-27.

  The United States uses mm/dd/yy and other countries use dd/mm/yy
  \cite{cms17-ambiguous-dates}.
  I recommend using what your bibliography style defines
  or the unambiguous ISO 8601 standard yyyy-mm-dd
  \cite{cms17-iso-dates}.%
}

\bug{4}{done}
Change citation, e.g., |[6], [71]| to |[6,71]|.
{\small
  Reported by Mark Senn on 2021-04-07.
  Fixed on 2022-04-14.
  Tested ok on 2022-04-14.%
}

\bug{5}{done}
Change citation, e.g., |[6], [7], [8]| to |[6-8]|.
{\small
  Reported by Mark Senn on 2021-04-07.
  Fixed on 2022-04-14.
  Tested ok on 2022-04-14.%
}

\bug{7}{fixed}
Non-nested description environments have bold items.
Nested description environments have non-bold items.
How come?
Are the indentations correct?
{\small
  Reported by Mark Senn on 2021-04-09.
  Tested ok on 2021-05-31.%
}

\bug{9}{done}
Check that |@{}| is before the left column
and after the right column in all tables.
{\small
  Reported by Mark Senn on 2021-04-19.
  Tested ok on 2022-10-18 using\hfil\break
  \verb+alias g=grep+\hfil\break
  \verb+g -P '^\s*\\begin{tabular}' *.tex | g -Pv '^.*?:\s*\\begin{tabular}{@{}.*?@{}}'+%
}

\bug{11}{answered}
Bibliography change:
Change,
for example,
``Acoustical Science and Technology, vol.~23, no.~1''
to
``Acoustical Science and Technology {\bfseries 23\/} ({\bfseries 1\/})''.
{\small
  Reported by Daniel Joesph Carr on 2021-06-16.
  Answered by Mark Senn on 2022-10-18.

  The
  \citetitle{ieee-reference-guide}
  \cite[page~12]{ieee-reference-guide}
  specifies that |vol.|~and |no.|~should be used.
  You are the only one that has requested this.
  I'm not going to change anything because of that.
  I like the succinct ``{\bfseries 23\/} ({\bfseries 1\/})''
  format but am not going to implement it because not
  everyone will know those are the journal volume and number.
}

\bug{12}{answered}
Bibliography change:
Change,
for example,
{\tt M.~Abramowitz and I.A.~Stegun, Eds.,}
to
{\tt M.~Abramowitz and I.A.~Stegun, editors,}
{\small
  Reported by Daniel Joesph Carr on 2021-06-16.
  Answered by Mark Senn on 2022-10-18.

  The
  \citetitle{ieee-reference-guide}
  \cite[page~5]{ieee-reference-guide}
  specifies that |Ed.|~for a single editor
  and |Eds.|~for multiple editors be used.

  You are the only one that has requested this.
  I'm not going to change anything because of that.

  But,
  if you put the current ieee.bbx file
  in the same directory as your thesis
  and change
  \verb+editor = Ed\adddot+
  to
  \verb+editor = editor\adddot+
  and
  \verb+editors = Eds\adddot+
  to\hfil\break
  {\tt editors = editors\char'134 adddot}
  it may do what you want.
  Email
  |latex@ecn.purdue.edu|
  if you need the current ieee.bbx file.
  I have not tested this answer.
}

\bug{16}{fixed}
Add DTECH degree.
{\small
  Reported by Mark Senn on unknown date.
  Program ``Technology''
  and degree ``Doctor of Technology'' worked ok
  on 2022-08-26.%
}

\bug{17}{fixed}
Allow |,| (comma) in |\title|.
{\small
  Reported by Mark Senn on unknown date.
  Tested ok on 2021-11-30.%
}

\bug{18}{fixed}
Allow |\\| in |\title|.
{\small
  Reported by Mark Senn on unknown date.
  Tested ok on 2021-11-30.%
}

\bug{22}{fixed}
|\H{o}| works in
\pdfLaTeXLogo\ but does not work in \LuaLaTeXLogo.
{\small
  Reported by Raymond Polak III on 2022-10-28.
  Use |\H{o}| to get \H{o} in the text.
  Use |\ZZH{o}| to get \H{o} in the bibliography.
  Tested ok on 2023-03-27.%
}

\bug{23}{fixed}
The
|Department of Human Development and Family Studies|
was renamed to
|Department of Human Development and Family Science|.
{\small
  Reported by Mark Senn on 2022-12-03.
  Fixed on 2024-06-12.
}

\bug{27}{done}
The figures in subsections
\ref{ss:counter-example}
and
\ref{ss:fourier-transform-example}
are\\
\hbox to \hsize{
  \hss
  \begin{tabular}{@{}lll@{}}
    \toprule
    \bf Color& \bf On Operating Sytem& \bf Using\\
    \midrule
    color& macOS 12.6.2& Firefox 108.0.2 (64-bit)\\
    color& Ubuntu 22.04 LTS& evince (GNOME Document Viewer 42.3)\\
    black and white& Ubuntu 22.04 LTS& Firefox 108.0.2 (64-bit)\\
    \bottomrule
  \end{tabular}
  \hss
}\\
{\small
  Reported by Mark Senn on 2023-01-11.
  Use software that will show the colors correctly.%
}

\bug{32}{fixed}
The first two pages of the thesis
(the title page
and the graduate school statement of committee approval)
should have a top margin of 1 1/2 \si{\in}.
{\small
  Reported by Lisa Williams on 2023-12-08.
  % Lisa Williams <will2922@purdue.edu>
  Fixed on 2024-02-07.
  Tested ok on 2024-02-07.%
}

\bug{35}{done}
Is there an easy way of dividing the thesis into multiple parts?\\
{\small
  Asked by Vahid Tac on 2024-05-29.
  Thesis Help (Lisa Williams) <thesishelp@purdue.edu>
  wrote on 2024-06-04
  ``Since it is not part of the thesis structure in Purdue policies,
  we do not want parts\ldots''.%
  % See
  %   /home/pier/e/queue/Mail/archives/latex/YM2406/8
  % for the queue item and
  %   ~/PurdueThesis/template/part.tex
  % for notes on how to implement \part.
}

