\ProvidesFile{ap-frequently-asked-questions}[2024-10-31 frequently asked questions appendix]

\newcommand{\MyA}{\textbf{A: }}

\makeatletter
\newcommand{\faq}[2]
  {%
    \vspace{6pt}
    \noindent
    {%
      \bfseries
      \ifthen{\equal{high}{#2}}{\color{red}}%
      \ifthen{\equal{low}{#2}}{\color{blue}}%
      \ifthen{\equal{answered}{#2}}{\color{black}}%
      \ifthen{\equal{done}{#2}}{\color{black}}%
      \ifthen{\equal{fixed}{#2}}{\color{black}}%
      \ifthen{\equal{wait}{#2}}{\color{black}}%
      \ifthen{\equal{not}{#2}}{\color{gray}}%
      {\fontsize{9}{10}\reset@font\bf FAQ}
      #1.
    }%
    \ignorespaces
  }
\makeatother
  
\chapter{FREQUENTLY ASKED QUESTIONS}

This appendix lists all frequently asked questions.
Each frequently asked question is assigned a number when I learn of it.
FAQ numbers are 1, 2,~\ldots\,.
I started keeping track
of frequently asked questions
in this fashion
on March 1, 2022.

\begin{tabular}{@{}ll@{}}
  \toprule
  \bf Description& \bf Color\\
  \midrule
  done or waiting on someone else& \color{black}black\\
  high priority or easy to do& \color{red}red\\
  low priority& \color{blue}blue\\
  not prioritized yet& \color{gray}gray\\
  \bottomrule\\
\end{tabular}

See the
|ap-frequently-asked-questions.tex|
file
for the \LuaLaTeXLogo\ input
for this appendix.


\section{These questions need to be answered}


\section{These questions are waiting on a reply from someone other than Mark Senn}


\section{These questions have been answered}

The subsection headings below are what part of the document
the question is about.


\subsection*{Everywhere}
\faq{1}{done}
The \LaTeXLogo\ input\\
\I2 \verb+$a | b$+\qquad
(Mark Senn recommends using \verb+\(a | b\)+ instead)\\
%   {\tt\char'134(\$a \char'174\ \$b\char'134)}
%   instead%
% )\\
gives\\
\I2 |! LaTeX Error: Command \ttfamily invalid in math mode.|\\
Reported by Negin Karisani.\\
\MyA
In thesis.tex, change\\
\I2 \verb+\DefineShortVerb{\|} % so "|verbatim|" will be verbatim+\\
% {\tt
%   \char'134 DefineShortVerb%
%   \{\char'134\char'174\}\ \ %
%   \% so "\char'174 verbatim\char'174" will be verbatim%
% }\\
to\\
\I2 \verb+% \DefineShortVerb{\|} % so "|verbatim|" will be verbatim+
% {\tt
%   \%\ \char'134 DefineShortVerb%
%   \{\char'134\char'174\}\ \ %
%   \% so "\char'174 verbatim\char'174" will be verbatim%
% }


\faq{5}{done}
When using Overleaf on Firefox
I get a gratuitous `\Box'
in the upper-left corner of each page.\\
\MyA
Resetting Firefox
(warning: this resets lots of stuff)
using the following steps
worked for me:\\
\I2 1. Select \Menu{Help > Troubleshoot Mode}.\\
\I2 2. Click \Keys{Restart}.\\
\I2 3. Click \Keys{Refresh Firefox}.\\
\I2 4. Click \Keys{Refresh Firefox}.\\
\I2 5. Click \Keys{Let's Go}.


\subsection*{Table of Contents}

\faq{2}{done}
I want text instead of page number to be the link
in the table of contents.
Asked by Danushka Menikkumbura on 2022-03-11.\\
\MyA
In PurdueThesis.cls change \verb+linktoc = page+
to \verb+linktoc = section+.
I do not recommend doing this because
\begin{itemize}
  \item
    you'll need to put this change
    in new PurdueThesis.cls files in the future
  \item
    people are used to using page numbers instead
    of chapter/section/etc.~titles for where they
    start
\end{itemize}


\subsection*{Chapters}
\faq{6}{done}
Sections are numbered 2.1, 2.2, 2.3, 2.1 using |\chapterappendix|.
They should be numbered 2.1, 2.2, 2.3, 2.A.
How do I fix this?
Asked by Ryan Hastings on 2024-10-28.\\
\MyA                                                                                    
Change\\
\I2|\chapterappendix|\\
to\\
\I2|\chapterappendix|\\
\I2|\renewcommand{\thesection}{\thechapter.\AlphAlph{\value{section}}}|
                                                                                    
This was fixed in the new PurdueThesis software
that was put on Overleaf
around October 25, 2024.
It contains lots of changes
but I suggest you do not update to it
if you plan to graduate in December 2024---%
you'd need to read and make some updates to your
PurdueThesis.cls, thesis.tex, and front.tex files.                                  


\subsection*{References}
\faq{4}{done}
I have an
|@online{|\ldots
reference with no
|date = {|\ldots|}|
and `()' gets printed in the references
around where the date would go.
How can I prevent the `()'
from getting printed.
Asked by Pratith Narasimha Shenai on 2023-07-15.
\MyA
Use
|@online[*]{|\ldots
instead of
|@online{|\ldots\,.
I don't know why this works.


\subsection*{Appendix}

\faq{3}{done}
Label Appendix/Appendices with APPENDIX.
Asked by Panos Manganaris % Panayotis Thalis Manganaris <pmangana@purdue.edu>
on 2023-06-16.
\MyA
Mark Jaeger,
former Manager
of the Thesis and Dissertation Office,
wrote and said
that the most important thing
in a thesis was
`consistency,
consistency,
consistency'.

For consistency,
\begin{itemize}
  \item
    Chapters aren't labeled with `CHAPTER'
    so
    Appendix/Appendices aren't labeled with `APPENDIX'.
  \item
    Chapters are listed as 1,~2,~\ldots\ %
    and appendices are listed as A,~B,~\ldots\ %
    in the Table of Contents.
\end{itemize}

Contemporary usage is to not label
chapters or appendices see MIT theses
\cite{jiang2022,stehr2022},
Stanford theses
\cite{guikema2004,simper2022},
and \TeXLogo/\LaTeXLogo documentation
\cite{kime2022,knuth2012,lamport1994}.
% Lisa Williams <will2922@purdue.edu> wrote on 2023-06-27 at 14:59-04:
% Appendix headings are on the list to discuss for consistency.
