\ProvidesFile{ch-introduction.tex}[2025-01-16 introduction chapter]


\chapter{INTRODUCTION}


\section{Typographic Conventions}

{
  \newlength{\Parindent}
  \setlength{\Parindent}{\parindent}
  \newcommand{\Indent}{\advance\leftskip by \Parindent}
  \parindent = 0pt

  \newcommand{\Describe}[2]{%
    {\Indent \Indent #1\endgraf}%
    {\Indent \Indent \Indent #2\endgraf}%
  }

  {%
    \Indent The following typographic conventions
    are used in this document.
    These conventions were influenced by
    \cite{wireshark-users-guide,dijk2000,weh2016}.
    There are no quotes in the typographic conventions.\endgraf
  }

  % Admonitions information is in \cite{wireshark-users-guide}.
  % Admonitions are not supported yet.

  % Dialog and window buttons information is in \cite{wireshark-users-guide}.
  % Dialog and window buttons are not supported yet.

  \Describe
  {\Emph{Emph}, \FirstTime{FirstTime}, and \Title{Title}}
  {%
    Emphasized material,
    terms used for the first time,
    and titles are typset in italics.
    Here are some examples:
    Emphasis: You \Emph{must} do this.
    First Time Use: An \FirstTime{ekayak}
    is an electric kayak.
    Title: He read \Title{The Grapes of Wrath}
    and watched \Title{Citizen Kane}.%
  }

  \Describe
  {\Keys{Keyboard} \Keys{Keys} and \Keys{Screen} \Keys{Buttons}}
  {%
    Keyboard keys look like keyboard keys.
    \Keys{Control + A} means press the Control key and A key at the same time.
    \Keys{A} \Keys{B} means press the A key and then press the B key.
    Screen Buttons look like screen buttons.%
  }

  % Can't use \verb iside an arguement to \Describe.
  \Describe
  {{\tt Literal Element}}
  {%
    Literal elements are typeset in a typewriter font.
    Literal elements include checkboxes,
    code,
    environment variables,
    file names,
    function names,
    \LaTeX\ input,
    output,
    variable names,
    and verbatim input (except for commands typed on the command line).
    {\tt\char'40} is used to indicate a space
    if it is not clear where spaces are.%
  }
  \index{.@"\verb*+ + (visible space)}
  \index{"\verb+"\char'40+}

  \Describe
  {\Menu{Menu > Submenu > Item}}
  {%
    Menus are typeset as arrows pointing to the right.
    For exmaple,
    to make sure smooth scrolling is on go to
    \Menu{Edit > Settings}
    and make sure the
    {\tt Use smooth scrolling\/}
    checkbox is checked.%
  }

  \Describe
  {\Place{Placeholder}}
  {%
    Placeholders are typset in a slanted font.
    Placeholders need to replaced with real input.%
  }

  \Describe
  {\Shell{shell command}}
  {%
    Shell commands are typset in a bold typewriter font.
    Shell commands are typed on the command line by the user.%
  }

}


\section{Writing in English Information}

\subsection{Don't use redundant acronyms}

Don't use redundant acronyms
\cite{
  fun-with-words2023,
  rome2020,
  redundant-acronym-phrases,
  knight,
  ras-syndrome,
  lrdg2020,
  everhart,
  cox2018%
}
like the following in
formal writing:

{
  \ZZbaselinestretch{1}
  \noindent
  \begin{longtable}{@{}ll@{}}
      \caption{Redundant Acronyms}\\
      \toprule
      \bfseries Redundant Acronym& \bfseries Corresponding Phrase\\
      \hline
    \endfirsthead
      \caption[]{\emph{continued}}\\
      \midrule
      \bfseries Redundant Acronym& \bfseries Corresponding Phrase\\
      \midrule
    \endhead
      \hline
      \multicolumn{2}{r}{\emph{continued on next page}}
    \endfoot
      \bottomrule
    \endlastfoot
    \% APR&               percent Annual Percentage Rate\\
    ABS system&           Antilock Braking System system\\
    AC current&           Alternating Current current\\
    ACT test&             American College Test test\\
    ADD disorder&         Attention Deficit Disorder disorder\\
    AIDS syndrome&        Acquired Immune Deficiency Syndrome syndrome\\
    AM modulation&        Amplitude Modulation modulation\\
    APL language&         A Programming Language languge\\
    APR rate&             Annual Percentage Rate rate\\
    ATM machine&          Automated Teller Machine machine\\
    BASIC code&           Beginner's All-Purpose Symbolic Instruction Code code\\
    CAD design&           Computer-Aided Design design\\
    CD disc&              Compact Disc disc\\
    CNN news network&     Cable News Network news network\\
    COBOL language&	      Common Business-Oriented Language language\\
    DC Comics&            Detective Comics Comics\\
    DC current&           Direct Current current\\
    DVD disk&             Digital Versatile Disk disk\\
    DMZ zone&             DeMilitarized Zone zone\\
    FOD damage&           Foreign Object Damage damage\\
    GIF format&           Graphics Interchange Format format \cite{merriam-webster-gif}\\
    GMT time&             Greenwich Mean Time time \cite{merriam-webster-gmt}\\
    GPS system&           Global Positioning System system \cite{merriam-webster-gps}\\
    GOP party&            Grand Old Party party \cite{merriam-webster-gop}\\
    GRE exam&             Graduate Record Examination exam \cite{merriam-webster-gre}\\
    HIV virus&            Human Immunodeficiency Virus virus \cite{merriam-webster-hiv}\\
    HTML language&        HyperText Markup Language language \cite{merriam-webster-html}\\
    IRA account&          Individual Retirement Account account \cite{merriam-webster-hiv}\\
    ISBN number&          International Standard Book Number number\\
    ISDN network&         Integrated Services Digital Network network\\
    LAN network&          Local Area Network network\\
    LCD display&          Liquid Crystal Display display\\
    LED diode&            Light Emitting Diode diode\\
    LEM module&           Lunar Excursion Module module\\
    MLB baseball&         Major League Baseball baseball \cite{merriam-webster-mlb}\\
    MIDI interface&       Musical Instrument Digital Interface interface\\
    MLS soccer&           Major League Soccer soccer \cite{merriam-webster-mlb}\\
    NATO organization&    North Atlantic Treaty Organization organization\\
    NPR radio&            National Public Radio radio\\    % https://www.curtishoneycutt.com/blog/2019/5/14/tips-on-avoiding-ras-syndrome
    OPEC countries&       Organization of Petroleum Exporting Countries countries\\  % https://www.etymologynerd.com/blog/redundant-acronyms-that-are-redundant
    PAC committee&        Political Action Committee committee\\       % https://www.curtishoneycutt.com/blog/2019/5/14/tips-on-avoiding-ras-syndrome
    PC computer&          Personal Computer computer\\
    PDF format&           Portable Document Format format \cite{merriam-webster-pdf}\\
    PIN number&           Personal Identification Number number\\
    RAM memory&           Random-Access Memory memory\\
    SSN number&           Social Security Number number \cite{merriam-webster-ssn}\\
    TCP-IP protocol&      Transmission Control Protocol/Internet Protocol protocol\\  % https://systemato.com/blog/redundant-acronyms-make-you-look-stupid-even-if-you-arent/
    UPC code&             Universal Product Code code\\
    UL laboratories&      Underwriters Laboratories laboratories\\
    VAT tax&              Value Added Tax tax\\
    VHF frequency&        Very High Frequency frequency\\
    VIN number&           Vehicle Identification Number number\\
  \end{longtable}
}

I sometimes use FBI
(Federal Bureau of Investigation)
as an adjective, e.g.,
`an FBI investigation'.

The SAT (SAT in not an acronym) is a standardized test
\cite{sat}.

\subsection{Logical punctuation}
\ix{logical punctuation}

I use logical punctuation
\cite{yagoda2011}:\\
  \I2 The sign said ``Buses Only''.\\
instead of\\
  \I2 The sign said ``Buses Only.''\\
so quoted material,
and only quoted material,
is inside quotes.
This is relatively new and not many people use it.
Your major professor may not like this style.
Check with them before you decide to use this.


\subsection{Serial comma}
\ix{, (comma)//comma//serial comma}

I use the serial comma:\\
  \I2 apple, berry, and cherry\\
instead of\\
  \I2 apple, berry and cherry\\
because I find it easier
to see the list items
when they are separated by commas.
The serial comma is also known as the
Oxford comma,
Harvard comma,
or series comma.


\subsection{Modern pronouns}

I don't use modern pronouns in this document
but if I did I'd use the LambdaMoo ``spivak'' (1991)
\cite{spivak-pronoun}
variant of gender-neutral pronouns.
(Hmm\ldots
thinking machines are coming.
People are anthropocentric \cite{merriam-webster-anthropocentric}.
There may be resistance to
using traditional human pronouns
for machines that think.
I wonder if using tradutional
pronouns for mostly-meatbag lifeforms
and spivak pronouns for mostly non-meatbag
lifeforms would make sense.)

\vspace{6pt}
{
  \ZZbaselinestretch{1}
  \let\B=\bfseries
  \begin{tabular}{llllll}
    \B Variant&
      \B Subject&
      \B Object&
      \(\vcenter{%
        \hbox{\strut\B Possessive}
        \hbox{\strut\B adjective}
      }\)&
      \(\vcenter{%
        \hbox{\strut\B Posessive}
        \hbox{\strut\B pronoun}}\)&
      \B Reflexive\\[18pt]
    \B Masculine&
      he said&
      I saw him&
      his leg hurt&
      that is his&
      he hurt himself\\[6pt]
    \B Feminine&
      she said&
      I saw her&
      her leg hurt&
      that is hers&
      she hurt herself\\[6pt]
    \(\vcenter{%
      \hbox{\strut\B LambdaMoo}
      \hbox{\strut\B ``spivak'' (1991)}
    }\)&
      e said&
      I saw em&
      eir leg hurt&
      that is eirs&
      e hurt emself\\
  \end{tabular}
}
\vspace{6pt}


\section{The software used}

Prof.~Donald Knuth\ix{Knuth, Donald Ervin}
of Stanford University
wrote the \FirstTime{\TeXLogo\/}\ix{\TeX}
typesetting system
for the creation of beautiful books---%
and especially for books that contain lots of mathematics
\cite[page v]{knuth2012}.
He wasn't happy with the quality of the typesetting in his
multi-volume
\emph{The Art of Computer Programming}.
\TeXLogo\ was first released in 1978.
\TeXLogo-related\ systems are not
`What You See Is What You Get'
(WYSIWYG) systems.
Documents are created in an ordinary text editor
and processed by a program to make the output.
This is a nice feature because one can concentrate on the content
of the document instead of the appearance
of the document.

Dr.~Leslie Lamport\ix{Lamport, Leslie B.}
extended \TeXLogo\ using \TeXLogo's
programming language to make the easier-to-use {\sl\LaTeXLogo}\ix{\LaTeXLogo}.
It was first released in 1984.
The \LaTeXLogo\ Project
\cite{thelatexproject2023}
now handles \LaTeXLogo\ development.

\FirstTime{\LuaLaTeXLogo\/}\ix{\LuaLaTeXLogo}
is a dialect of \LaTeXLogo\ with features
that make it easier to use for programming.

\FirstTime{\TeXLiveLogo\/}\ix{\TeXLiveLogo}
\cite{texlive}
is a free \TeXLogo\ software distribution
that contains all of the above software and more.
This document was created using \TeXLiveLogo.
\TeXLiveLogo\ is available for Linux,
Unix,
and Windows.
\FirstTime{\MacTeXLogo\/} is a \TeXLiveLogo-based system for Apple MacOS computers.
\FirstTime{\OverleafLogo\/} is a \TeXLiveLogo-based system to run \TeX\ on the web.

\FirstTime{\PurdueThesisLogo\/}
(\FirstTime{\PuThLogo\/} for short---rhymes with tooth)
uses \LuaLaTeXLogo\ to
make it easier to do
Purdue theses,
dissertations,
etc.
This template demonstrates how to use \PurdueThesisLogo.
\PurdueThesisLogo\ is intended to support all Purdue campuses,
programs,
and graduate degrees.
I only support this software using \TeXLiveLogo.

Figure \ref{fi:lualatex-system-flowchart} shows the \LuaLaTeXLogo\ system flowchart.
\FirstTime{Overleaf\/}
\cite{overleaf}
uses latexmk
\cite{latexmk}
to run
|biblatex|,
|makeindex|,
and |lualatex| automatically
so the minimum amount of work is done.
On Linux,
MacOS,
and Windows you can run the programs individually
or use |latexmk|---I recommend using |latexmk|.

\begin{figure}
  \centering
  \begin{tikzpicture}

    \tikzset{font={\fontsize{10pt}{12pt}\selectfont}}

    % Large rectangle.
    \coordinate (pdflatex-nw-c) at (0,8);  \coordinate (pdflatex-ne-c) at (6,8);
    \coordinate (pdflatex-sw-c) at (0,0);  \coordinate (pdflatex-se-c) at (6,0);

    % Draw large rectangle.
    \draw (pdflatex-sw-c) -- (pdflatex-nw-c) -- (pdflatex-ne-c) -- (pdflatex-se-c) -- cycle;

    % West edge of rectangle.
    \coordinate (my-fonts-c)       at (0,7);  \coordinate (my-fonts-w-c)     at ($(my-fonts-c)     + (-1,0)$);
    \coordinate (my-images-c)      at (0,6);  \coordinate (my-images-w-c)    at ($(my-images-c)    + (-1,0)$);
    \coordinate (my-packages-c)    at (0,5);  \coordinate (my-packages-w-c)  at ($(my-packages-c)  + (-1,0)$);
    \coordinate (my-tex-files-c)   at (0,4);  \coordinate (my-tex-files-w-c) at ($(my-tex-files-c) + (-1,0)$);
    \coordinate (w-aux-files-c)    at (0,3);  \coordinate (w-aux-files-w-c)  at ($(w-aux-files-c)  + (-1,0)$);
      \coordinate (w-aux-files-w-w-c) at ($(w-aux-files-w-c) + (-1,0)$);
    \coordinate (bbl-files-c)      at (0,2);  \coordinate (bbl-files-w-c)    at ($(bbl-files-c)    + (-1,0)$);
    \coordinate (ind-file-c)       at (0,1);  \coordinate (ind-file-w-c)     at ($(ind-file-c)     + (-1,0)$);

    % North edge of rectangle.
    \coordinate (system-fonts-c)    at (1.6,8);  \coordinate (system-fonts-n-c)    at ($(system-fonts-c)    + (0,1)$);
    \coordinate (system-packages-c) at (4.4,8);  \coordinate (system-packages-n-c) at ($(system-packages-c) + (0,1)$);

    % East edge of rectangle.
    \coordinate (log-file-c)      at (6,6);  \coordinate (log-file-e-c)      at ($(log-file-c) + (1,0)$);
    \coordinate (my-pdf-file-c)   at (6,4);  \coordinate (my-pdf-file-e-c)   at ($(my-pdf-file-c) + (1,0)$);
    \coordinate (e-aux-files-c)   at (6,3);  \coordinate (e-aux-files-e-c)   at ($(e-aux-files-c) + (1,0)$);
      \coordinate (e-aux-files-e-e-c)         at ($(e-aux-files-e-c) + (1,0)$);

    % Draw arrows on west side.
    \draw [thick, ->]       (my-fonts-w-c)     -- (my-fonts-c);
    \draw [thick, ->]       (my-images-w-c)    -- (my-images-c);
    \draw [thick, ->]       (my-packages-w-c)  -- (my-packages-c);
    \draw [ultra thick, ->] (my-tex-files-w-c) -- (my-tex-files-c);
    \draw [thick, ->]       (w-aux-files-w-c)  -- (w-aux-files-c);
    \draw [thick, ->]       (bbl-files-w-c)    -- (bbl-files-c);
    \draw [thick, ->]       (ind-file-w-c)     -- (ind-file-c);

    % Draw arrows on north side.
    \draw [thick, ->] (system-fonts-n-c)    -- (system-fonts-c);
    \draw [thick, ->] (system-packages-n-c) -- (system-packages-c);

    % Draw arrows on east side.
    \draw [thick, ->]       (log-file-c)    -- (log-file-e-c);
    \draw [ultra thick, ->] (my-pdf-file-c) -- (my-pdf-file-e-c);
    \draw [thick, ->]       (e-aux-files-c) -- (e-aux-files-e-c);

    % Print file extensions on west side.
    \draw (my-fonts-w-c)     node[rounded rectangle, draw, left] {my fonts};
    \draw (my-images-w-c)    node[rounded rectangle, draw, left] {my images};
    \draw (my-packages-w-c)  node[rounded rectangle, draw, left] {my packages};
    \draw (my-tex-files-w-c) node[rounded rectangle, draw, left] {my .tex files};
    \draw (w-aux-files-w-c)  node[rounded rectangle, draw, left] (w-aux-files-w-n) {.aux files};
    \draw (bbl-files-w-c)    node[rounded rectangle, draw, left] (w-bbl-files-w-n) {.bbl files};
    \draw (ind-file-w-c)     node[rounded rectangle, draw, left] (w-ind-file-w-n)  {.ind file};

    % Print labels on north side.
    \draw (system-fonts-n-c)    node[rounded rectangle, draw, above] {\begin{tabular}{c}system\\fonts\end{tabular}};
    \draw (system-packages-n-c) node[rounded rectangle, draw, above] {\begin{tabular}{c}system\\packages\end{tabular}};

    % Print file extensions on east side.
    \draw (log-file-e-c)      node[rounded rectangle, draw, right] {.log file};
    \draw (my-pdf-file-e-c)   node[rounded rectangle, draw, right] {my .pdf file};
    \draw (e-aux-files-e-c)   node[rounded rectangle, draw, right] (e-aux-files-e-n) {.aux files};

    % Print program names.
    \node at (3,4) {\large lualatex};
    \node[rectangle, draw] at (3,-1) (makeindex-n) {makeindex (make index)};
    \node[rectangle, draw] at (3,-2) (biber-n) {biber (make bibliography)};

    % Draw lines on west side of big rectangle.
    \draw [rounded corners, thick, <-] (w-aux-files-w-n.west) -- ++(-2,0)   -- ++(0,-6) -- (0,-3);
    \draw [rounded corners, thick, <-] (w-bbl-files-w-n.west) -- ++(-1.5,0) -- ++(0,-4) -- (biber-n.west);
    \draw [rounded corners, thick, <-] (w-ind-file-w-n.west)  -- ++(-1,0)   -- ++(0,-2) -- (makeindex-n.west);

    % Draw line on east side of big rectangle.
    \draw [rounded corners, thick, ->] (e-aux-files-e-n.east) -- ++(1,0) -- ++(0,-4) -- (makeindex-n.east);
    \draw [rounded corners, thick, ->] (e-aux-files-e-n.east) -- ++(1,0) -- ++(0,-5) -- (biber-n.east);
    \draw [rounded corners, thick]     (e-aux-files-e-n.east) -- ++(1,0) -- ++(0,-6) -- (0,-3);

  \end{tikzpicture}
  \caption{\LuaLaTeXLogo\ System Flowchart}
  \label{fi:lualatex-system-flowchart}
\end{figure}

The
Thesis and Dissertation Office
\cite{thesis-and-dissertation-office-resources}
wrote a formatting manual
\cite{thesis2017}
and Microsoft Word templates
\cite{thesis2020}
for Purdue theses,
etc.


\section{\LaTeX-related information}

\subsection{Input reading rules}

\LaTeXLogo\ uses the following rules when reading input:
\begin{itemize}
  \item
    Spaces at the beginning of a line are ignored.
  \item
    \Keys{\sffamily\%} starts a comment.
    The |%| and everything after it on that line are ignored.
    Type \Keys{\sffamily\char'134} \Keys{\sffamily\%} to print a `\%'.
  \item
    \Keys{Enter} is equivalent to a space.
  \item
    \Keys{Enter} \Keys{Enter} (a blank line) ends a paragraph.
  \item
    Typing multiple spaces works the same as one space.
\end{itemize}

% The itemize environment takes up lots of space---sometimes
% I like to compress the layuot as shown below.

\subsection{Input preparation conventions}

In \LaTeX\ typing

\begin{verbatim}
As \(h\) approaches 0 in the limit, the last fraction can be shown to go to
zero.  This is true because the area of the red portion of excess region is
less than or equal to the area of the tiny black-bordered rectangle.  More
precisely, \[\left|f(x)-\frac{A(x+h)-A(x)}h\right|-\frac{\left|\text{Red
Excess}\right|}h\le\frac{h\big(f(x+h_1)-f(x+h_2)\big)}h=f(x+h_1)-f(x+h_2),\]
where \(x+h_1\) and \(x+h_2\) are points where \(f\) reaches its maximum and
its minimum, respectively, in the interval \([x,x+h]\).
\end{verbatim}
\noindent gives exactly the same output as

\begin{verbatim}
As \(h\) approaches 0 in the limit,
the last fraction can be shown to go to zero.
This is true because the area of the red portion of excess region
is less than or equal to the area of the tiny black-bordered rectangle.
More precisely,
\[
  \left |
    f(x)
    -
    \frac {A(x+h)-A(x)} {h}
  \right |
  -
  \frac {\left|\text{Red Excess}\right|} {h}
  \le
  \frac {h\big(f(x+h_1)-f(x+h_2)\big)} {h}
  =
  f(x+h_1)
  -
  f(x+h_2),
 \]
 where \(x+h_1\)
 and \(x+h_2\) are points where \(f\) reaches its maximum and its minimum,
 respectively,
 in the interval \([x, x + h]\).
\end{verbatim}


I've used \LaTeX\ over~30 years
and use these personal conventions
to prepare input.
Using these conventions leads
to many short lines,
but I find those easier
to read and edit.
Do whatever works best for you.

\I2 start input lines with\\
  \I3 the first word of a sentence\\
  \I3 \verb+(+\\
  \I3 \verb+and+\\
  \I3 \verb+but+\\
  \I3 \verb+from+\\
  \I3 \verb+or+\\
  \I3 \verb+to+

\NL
\I2 end input lines with\\
  \I3 sentence-ending periods\\
  \I3 phrase-ending commas\\
  \I3 phrase-ending colons\\
  \I3 phrase-ending semicolons\\
  \I3 \verb+)+\\
  \I3 \verb+\\+\\
  \I3 \verb+\\[+\textit{dimension}\verb+]+

\NL
\I2 put these on a line of their own\\
  \I3 \verb+\begin{+\textit{environment name}\verb+}+\\
  \I3 \verb+\end{+\textit{environment name}\verb+}+\\
  \I3 short parenthetical remark


\section{Filenames}
\ix{filenames}

There are several different name styles for file names:\ix{camelCase//kebab-case//PascalCase//snake\_case}

{%
  \singlespace
  \I2
  \begin{tabular}{@{}ll@{}}
    \toprule
    \bf Name& \bf Why it's called that\\
    \midrule
    camelCase& |C| is taller that surrounding characters,
      looks like camel's hump\\
    kebab-case& letters appear to be slid on shish-kebab skewer,
      no \Keys{Shift} needed\\
    PascalCase& popular in the Pascal programming language\\
    snake\_case& looks like a snake, is kebab-case except
      |-| is changed to |_|\\
    \bottomrule
  \end{tabular}
}

\vspace*{6pt}
\textcolor{red}{I recommend you only use kebab-case file names}
that consist of only lowercase letters,
zero or more digits,
zero or more \verb+-+ characters
(but no consecutive \verb+-+ characters),
and a single period.
You won't need to use \Keys{Shift} then.

\textcolor{red}{Do not put spaces in your file names.}
It makes it easier to run your thesis on other computer operating systems.
Linux, MacOS, and Windows are operating systems.

I like
to start all chapter file names with |ch-|.
Chapter names are everything
from the beginning of the thesis through the last chapter.
Chapters include all front matter in addition
to all chapters.

Appendix names start with |ap-|
and are everything after the last chapter including any bibliography,
colophon,
indices,
and vita.

Graphics files specific to your thesis start
with \verb+gr-+ and go in the graphics folder.
Non-thesis graphics files retain their normal names
and go in the graphics folder.

\LaTeX\ package files specific to your thesis  start
with \verb+pa-+ and go in the packages folder.
Non-thesis packages retain their normal names
and go in the packages folder.


\section{Special input characters}

\UndefineShortVerb{\|}
\DefineShortVerb{\;}  % so ";verbatim;" will be verbatim
\noindent
{
  \setlength{\tabcolsep}{8.5pt}
\begin{tabular}{@{}lllllllllll@{}}
  \multicolumn{10}{@{}l}{These input characters are special:\hfil}\\
  \kern\parindent& ;#;&  ;$;&  ;%;&  ;&;&  ;\;&            ;^;&         ;_;&  ;{;&  ;};&  ;~;\\
  \multicolumn{10}{@{}l}{Type\hfil}\\
  \kern\parindent& ;\#;& ;\$;& ;\%;& ;\&;& ;$\backslash$;& ;\char'136;& ;\_;& ;\{;& ;\};& ;\char'176;\\
  \multicolumn{10}{@{}l}{to get this output\hfil}\\
  \kern\parindent& \#&   \$&   \%&   \&&   $\backslash$&   \char'136&   \_&   \{&   \}&   \char'176\\
\end{tabular}
}
\UndefineShortVerb{\;}
\DefineShortVerb{\|}  % so "|verbatim|" will be verbatim


\section{Spacing after periods}

A lowercase letter followed by a period\ix{. (period)//spacing!after period}
is treated like the end of a sentence
with approximately two spaces following the period.
To not make it the end of a sentence put \verb+\+
or \verb+~+ after the period.
See table below.

An uppercase letter followed by a period\ix{. (period)//spacing!after period}
is treated like a person's middle initial
with approximately one space following the period.
To make it the end of a sentence put \verb+\@+
before the period.
See table below.

\begin{singlespace}
  \begin{tabular}{@{}lll@{}}
    \toprule
    \bfseries Input& \bfseries Output& \bfseries Comment\\
    \midrule
    \noalign{\vspace{2pt}}
    \verb+Dr. Smith+& Dr. Smith& too much space after \verb+Dr.+\\
    \verb+Dr.\ Smith+& Dr.\ Smith& correct, \verb+Dr.+ and \verb+Smith+ can be on different lines\\
    \verb+Dr.~Smith+& Dr.~Smith& correct, \verb+Dr.+ and \verb+Smith+ will be on same line, I\\
    & & recommend using this\\
    \noalign{\vspace{6pt}}
    \verb+at NASA.  The+& at NASA.  The& not enough space after \verb+NASA.+\\
    \verb+at NASA\@.  The+& at NASA\@.  The& correct\\
    \bottomrule
  \end{tabular}
  \index{Dr.~Smith}
  \index{Smith}
  \index{\verb+~+ (tilde)}
  \index{tilde (\verb+~+)}
  \index{NASA}
  \index{\verb*+\ +}
  \index{\verb+"\"@+}
  \index{period!space after}
  \index{initials}
\end{singlespace}

\vspace{\baselineskip}

(%
  I thought the following was too confusing.
  One or more \emph{lowercase}/\emph{uppercase}
  letters followed by a period
  is treated like
  \emph{the end of a sentence}/\emph{a person's middle initial}
  with approximately
  \emph{two}/\emph{one}
  space(s) following the period.%
)\todowarn{maybe move this to writing style appendix?}

(%
  I thought some people might think the following
  is too informal or nonstandard.
  It is pretty confusing also.
  One or more
  \lower6pt\hbox{\rlap{\small lowercase}}%
  \raise6pt\hbox{\small uppercase}
  letters followed by a period
  is treated like
  \raise6pt\hbox{\rlap{\small a middle initial}}%
  \lower6pt\hbox{\small the end of a sentence}
  \noindent with approximately
  \raise6pt\hbox{\small \rlap{one}}%
  \lower6pt\hbox{\small two}
  space(s) following the period.%
)\todowarn{maybe move this to writing style appendix?}


\section{Five kinds of dashes}

There are five kinds of dashes\ix{dash}

\edef\The#1pt{#1}

\begin{singlespace}
  \newlength{\myhyphenlen}      \settowidth{\myhyphenlen}{-}
  \newlength{\myendashlen}      \settowidth{\myendashlen}{--}
  \newlength{\myemdashlen}      \settowidth{\myemdashlen}{---}
  \newlength{\myfiguredashlen}  \settowidth{\myfiguredashlen}{\FigureDash}
  \newlength{\myminuslen}       \settowidth{\myminuslen}{\(-\)}
  \begin{tabular}{@{}llll@{}}
    \toprule
    \bfseries Name& \bfseries Input& \bfseries Output& \bfseries Width in Points (72.27 points/inch)\\
    \midrule
    hyphen& \verb+-+ (one hyphen)& -& \the\myhyphenlen\\
    endash& \verb+--+ (two hyphens)& --& \the\myendashlen\\
    emdash& \verb+---+ (three hyphens)& ---& \the\myemdashlen\\
    figure dash& \verb+\FigureDash+& \FigureDash& \the\myfiguredashlen\\
    minus sign& \verb+\(-\)+& \(-\)& \the\myminuslen\\
    \bottomrule
  \end{tabular}
\end{singlespace}

\begin{description}

  \item[hyphen]
  \ix{dash//hyphen//dash!hyphen}
    The hyphen
    is a punctuation mark used to join words
    and to separate syllables of a single word
    \cite{wikipedia-hyphen}.
    \begin{singlespace}
      \begin{tabular}{@{}lll@{}}
        \toprule
        \bfseries Input& \bfseries Output& \bfseries Comment\\
        \midrule
        \verb+-+ (one hyphen)& -\\
        \verb+son-in-law+& son-in-law& used to join words\\
        \verb+gas-oline+& gas-oline& used to separate syllables, \LaTeX\ hyphenates words\\
        & & automatically so you may not ever use this\\
        \bottomrule
      \end{tabular}
    \end{singlespace}

  \item[endash]
  \ix{dash//endash//dash!endash}
    The endash
    \cite{wikipedia-endash}
     is used for
    \begin{singlespace}
      \begin{tabular}{@{}lll@{}}
        \toprule
        \bfseries Input& \bfseries Output& \bfseries Comment\\
        \midrule
        \verb+--+ (two hyphens)& --\\
        \verb+The Purdue--IU game+& The Purdue--IU game& conflict\\
        \verb+Perth--Dubai--Boston+& Perth--Dubai--Boston& connection\\
        \verb+Teal Road runs East--West+& Teal Road runs East--West& direction\\
        \verb+ages 21--65+& ages 21--65& age range\\
        \verb+June--July 1967+& June--July 1967& month range\\
        \verb+pages 38--55+& pages 38--55& page range\\
        \verb+1:15--2:15 p.m.+& 1:15--2:15 p.m.& time range\\
        \verb+Purdue beat IU 35--28+& Purdue beat IU 35--28& scores\\
        \bottomrule
      \end{tabular}
    \end{singlespace}

  \item[emdash]
  \ix{dash//emdash//dash!emdash}
    The emdash
    \cite{wikipedia-emdash}
     is used for
    \begin{singlespace}
      \begin{tabular}{@{}ll@{}}
        \toprule
        \verb+---+ (three hyphens)& ---\\[6pt]
        \bfseries Input& \verb+the usual suspects---Larry, Moe, and Curly+\\
        \bfseries Output& the usual suspects---Larry, Moe, and Curly\\
        \bfseries Comment& --- acts like colon\\[6pt]
        \bfseries Input& \verb+Larry, Moe, and Curly---the usual suspects+\\
        \bfseries Output& Larry, Moe, and Curly---the usual suspects\\
        \bfseries Comment& inverse function of colon\\[6pt]
        \bfseries Input& \verb+three people---Larry, Moe, and Curly---%+\\
        & \verb+are the usual suspects+\\
        \bfseries Output& three people---Larry, Moe, and Curly---are the usual suspects\\
        \bfseries Comment& first --- acts as \verb+(+, second --- acts as \verb+)+\\[6pt]
        \bfseries Input& \verb+I believe I shall---no, I'm going to do it.+\\
        \bfseries Output& I believe I shall---no, I'm going to do it.\\
        \bfseries Comment& use --- when a thought evolves on the fly\\
        \bottomrule
      \end{tabular}
    \end{singlespace}

    Emdashes should be used sparingly in formal writing.

  \item[figure dash]
  \ix{dash//figure dash//dash!figure dash}
    The figure dash
    (input: \verb+\FigureDash+)
    is used to separate digits---it's the same width
    as a digit and is used in identification numbers,
    part numbers,
    phone numbers, etc.
    Type, for example, \verb+Q6759\FigureDash 18100+
    to get ``Q6759\FigureDash 18100''.

  \item[minus sign]
  \ix{dash//minus sign//dash!minus sign}
    Used for negative numbers or subtraction in math mode.
    \begin{singlespace}
      \begin{tabular}{@{}lll@{}}
        \toprule
        \bfseries Input& \bfseries Output& \bfseries Comment\\
        \midrule
        \verb+-+& \(-\)& (one hyphen in text math mode or display math mode)\\
        \verb=\(-a + b\)=& \(-a + b\)& negative $a$\\
        \verb+\(a - b\)+& \(a - b\)& subtraction\\
        \bottomrule
      \end{tabular}
    \end{singlespace}

\end{description}

% The first use of an unusual term is \FirstTime{emphasized}.
% It is defined soon after it is emphasized.
% From http://everets.org/kevin/ten-codes.php retrieved on 2020-02-28:
%     CODE  MEANS
%     10-7  Out of service
% So, the model number is a joke.
% 10\FigureDash 7
% for this research.
